Democracy, Public Support, and Measurement Uncertainty

### 2021-08-11 paper/dcpo_demsupport.Rmd
updating memo on random walk.

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 12pt
indent: true
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
---

@@

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300
)

@@

# load(here("data", "correct_cls_ajps.rda"))
# load(here("data", "correct_cls_apsr.rda")) 
# load(here("data", "expcor_cls_ajps.rda"))
# load(here("data", "expcor_cls_apsr.rda"))

@@

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
(See more details in Online Supplementary Material \@ref(dgp).)
Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference.

## Uncertainty Incorporation

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p. 18; @Gandhi2020, p. 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp. 791-792; @caughey2018, p. 254]. 
Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error. 
We conduct inferences from the distributive data via a technique known as "method of composition" (MOC) [@Treier2008, p. 215].
See more details of the method and the operational process in Online Supplementary Material \@ref(moc).

```{r compare_n}

@@

In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models or controlling for corruption alter the conclusion (see Online Supplementary Material \@ref(moc) for the the result of the full-pack analyses).

@@

Moreover, the results expose another risk for ignoring uncertainty: missestimation. 
As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
Methodologically, the shifts indicate that the 900 regressions of public support on democracy do not yield consistent results, although the explanatory and control variables were drawn from the same distribution. 
In this sense, the coefficients produced simply by the means of the variable distributions are no more than a one-time guess of the true parameters and apparently not a robust one. 
More importantly, what this methodological difference leads to is a substantively opposite conclusion of the relationship between public opinions and institutional democratization.
Our replication results manifest the uncertainty ignorance with mounting risk.

```{r pointAJPS}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r mocresult-pureAJPS, eval=FALSE}

@@

```{r mocresult-expAJPS, eval=FALSE}

```{r formatResult-AJPS}
result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
 mutate(MOCsumm(mocresult_correctAJPS[["pooled"]]), model = "W. Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")))

result_ajpsPooled <- result_pooledAJPS %>% 
    filter(type == "Pooled")

result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["pooled-regime"]]), model = "W. Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_correctAJPS[["gmm-regime"]]), model = "W. Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data")))

result_ajpsRegime <- result_regimeAJPS %>%
    filter(type == "Pooled") %>% 
    mutate(type = "Regime Specified")

```{r coefName-AJPS}
index_coefName <- c(
    `Democracy\n (t-1)` = "Democracy[t-1]",
    `Democracy\n (t-2)` = "Democracy[t-2]",
    `Support\n (t-1)` = "Support[t-1]",
    `Support\n demo only\n (t-1)` = "Support[t-1](demo~only)",
    `Support\n auto only\n (t-1)` = "Support[t-1](auto~only)",
    `Log GDP\n per capita\n (t-1)` = "Log~GDP~per~capita[t-1]",
    `GDP per\n capita growth\n (t-1)` = "GDP~per~capita~growth[t-1]",
    `Regional\n democracy\n (t-1)` = "Regional~democracy[t-1]",
    `Percent\n Muslim\n (t-1)` = "Percent~Muslim[t-1]",
    `Resource\n dependence\n (t-1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center'}

type_model <-
  c("Original", "W. Uncertainty", "Uncertainty+Expanded Data")

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
      legend.title = element_blank()
    ) +
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

The importance for taking the measurement uncertainty into account appear more evident when the relevant variable plays as the outcome variable. 
In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa. 
However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier

load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r mocresult-pureAPSR, eval=FALSE}

```{r mocresult-expAPSR, eval=FALSE}

```{r formatResult-APSR}
# Pooled---------------------------------------

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

result_apsrPooled <- result_APSR1 %>% 
    filter(type == "ECM") %>% 
    mutate(type = "Pooled")

# Institution----------------------------------

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled-regime1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd-regime1"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

result_apsrRegime <- result_RegAPSR1 %>% 
    filter(type == "ECM") %>% 
    mutate(type = "Institution Specified")

# Pooled-corruption------------------------------

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["pooled2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_correctAPSR[["fd2"]]), model = "W. Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","W. Uncertainty", "Uncertainty+Expanded Data"))
  )

# Institution Corruption--------------------------------

>>>>

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
---

@@

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  eval = FALSE,
  dpi = 300
)

@@

load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

@@

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

## Data Recollection and Incorporating Uncertainty
Despite the great effort of collecting data and identifying differences, we could not entirely achieve a primary replication [see @Grossman2020, p. 18] based on @Claassen2020a's Dataverse materials.
Our replication data has differences in number of country-year surveys and in sample size.
Specificially, we have five fewer observations, three of which are no longer available in originial survey data and two seem to have never existed, and one more survey item which was conflated in original data [see Online Supplementary Material].

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can bias coefficient estimates and standard errors.
Especially when measurement error is correlated with the outcome variable, the resulting bias could either attenuate or exaggerate the magnitude of the estimated effects [see, e.g., @Blackwell2017, p.360; @caughey2018, p.254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, p. 18; @Gandhi2020, p. 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, pp. 791-792; @caughey2018, p. 254].

Following this line, after replicating the original analyses with point estimates, we incorportate uncertainty in analysis models using our replication data.
We take the distribution of the latent (explanatory) variable, the outcome variable, and control variables to account for the uncertainty.
We take 900 draws from the posterior distribution of democratic support, outcome, and control variables with errors.
We then duplicate each article's analysis dataset of variables "without" measurement error 900 times, and assign them to each a different random draw from the distributions of variables with measurement error. 
We estimate each analysis model repeatedly on its respective collection of the datasets, and then make inferences from the distribution of parameter estimates by accounting for both within model standard error and between model variance.
This combine rule was set out in @Rubin1987, and has been employed in research of measurement errors [see, e.g., @Schnakenberg2014; @Crabtree2015] as well as incorporated in @Blackwell2017a's multiple overimputation (MO) to handle missing values and measurement uncertainty.
We also employ one alternative technique known as "method of composition" (MOC)  [@Treier2008, p. 215] as a robustness check [see Online Supplementary Material \@ref(moc)].

```{r compare_n, eval = TRUE}

@@

In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models and using MOC for uncertainty incorporation alters the conclusion (see Online Supplementary Material \@ref(fullAJPS), \@ref(fullAPSR), and \@ref(moc)).

@@

Moreover, the results also manfiest another risk of ignoring uncertainty: missestimation. 
As shown in Figure \@ref(fig:plot-mainAJPS), besides the confidence intervals the (point) estimates also shift. 
Methodologically, these shifts indicates that the 900 regressions of public support on democracy do not yield consistent results although the support opinions were drawn from the same distribution. 
In this sense, the coefficient produced simply by the mean of the public support distribution is no more than a one-time guess of the true parameter and definitely not a robust one. 
What this methodological issue lead to, however, is a substantively different conclusion of the relationship between public opinions and institutional democratization in both direction and magnitude.
The replication results illustrate the uncertainty ignorance with mounting risk.

```{r pointAJPS, eval=TRUE}
ls_iv <- c("plm::lag(SupDem_trim, 1)",
           "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)")

@@

```{r result-pureAJPS}
result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

  tidy_clsUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_clsUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_clsUncertain <- glance(result[[1]])
  }

  result_apsrAJPS <- list(tidy_clsUncertain, glance_clsUncertain)
})

names(result_pureAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_pureAJPS, file = here::here("output", "estimates_clsPureAJPS.RDS"))
```

```{r result-expAJPS}
result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  ## Not work with ifelse
  if(class(result[[1]])[1] == "plm"){
      result_vars <- mitools::MIextract(result, fun = vcovBK_se)
  }else{
      result_vars <- mitools::MIextract(result, fun = vcovHC_se)
  }

  tidy_dcpoUncertain <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  if(class(result[[1]]) == "plm"){ 
    glance_dcpoUncertain <- glance.plm(result[[1]]) # using the customized glance function
  }else{
    glance_dcpoUncertain <- glance(result[[1]])
  }

  result_expAJPS <- list(tidy_dcpoUncertain, glance_dcpoUncertain)
})

names(result_expAJPS) <- c("pooled", "pooled-regime", "gmm", "gmm-regime")

saveRDS(result_expAJPS, file = here::here("output", "estimates_clsExpAJPS.RDS"))
```

```{r coefName-AJPS, eval=TRUE}
index_coefName <- c(
  `plm::lag(Libdem_VD, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Libdem_VD, 1:2)2` = "Democracy[t-2]",
  `plm::lag(Vdem_libdem, 1:2)1` = "Democracy[t-1]",
  `plm::lag(Vdem_libdem, 1:2)2` = "Democracy[t-2]",
  `plm::lag(SupDem_trim, 1)` = "Support[t-1]",
  `plm::lag(theta, 1)` = "Support[t-1]",
  `plm::lag(SupDem_Democ, 1)` = "Support[t-1](demo~only)",
  `plm::lag(SupDem_Autoc, 1)` = "Support[t-1](auto~only)",
  `plm::lag(theta_dem_trim, 1)` = "Support[t-1](demo~only)",
  `plm::lag(theta_aut_trim, 1)` = "Support[t-1](auto~only)",
  `plm::lag(lnGDP_imp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP~per~capita[t-1]",
  `plm::lag(GDP_imp_grth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(mdprgdp_grwth, 1)` = "GDP~per~capita~growth[t-1]",
  `plm::lag(Libdem_regUN, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Region_libdem, 1)` = "Regional~democracy[t-1]",
  `plm::lag(Pr_Muslim, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(muslism_prop_2010, 1)` = "Percent~Muslim[t-1]",
  `plm::lag(Res_cp_WDI_di, 1)` = "Resource~dependence[t-1]",
  `plm::lag(dependence_pc_di, 1)` = "Resource~dependence[t-1]"
)
```

```{r plot-mainAJPS, fig.cap= "The Effect of Public Support on Democracy with Uncertainty", fig.width=7, fig.height=10, fig.align='center', eval=TRUE}

type_model <-
  c("Original", "Uncertainty", "Uncertainty+Expanded Data")

result_ajpsPooled <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$pooled[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_ajpsRegime <-
  list(result_clsAJPS,
       result_pureAJPS,
       result_expAJPS) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Regime Specified")

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
      legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    # scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

The importance of accounting for the measurement uncertainty appear more evident when the relevant variable plays as the outcome variable. 
In Figure \@ref(fig:plot-mainAPSR), we examine the thermostatic model of democratic support per @Claassen2020b [p. 47, Models 1.1 and 1.2]. 
When the uncertainty is ignored, the coefficient of $\Delta$liberal democracy (the uppermost set), the yearly changes of the institutional feature is negative inferring that the change in democratic mood decreases as change in democracy increases and vice versa. 
However, when the measurement uncertainty is properly accounted (the middle set), the point estimate shifts towards zero and the coefficient is no longer significant.
More data (the lowermost set), again, only adjusts the confidence intervals but not direction nor significance.

```{r pointAPSR, eval=TRUE}
load(here::here("data", "dem_mood_apsr.RData"))
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

@@

```{r result-pureAPSR}
result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_clsUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_clsUncertainAPSR <- glance.plm(result[[1]])

  result_apsrAJPSAPSR <- list(tidy_clsUncertainAPSR, glance_clsUncertainAPSR)
})

names(result_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2", "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_pureAPSR, file = here("output", "estimates_clsPureAPSR.RDS"))
```

```{r result-expAPSR}
result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

  result_betas <- mitools::MIextract(result, fun = coef)

  result_vars <- mitools::MIextract(result, fun = vcovHC_se)

  tidy_dcpoUncertainAPSR <- summary(mitools::MIcombine(results = result_betas, 
                             variance = result_vars)) %>% 
    rownames_to_column(var = "term") %>%
        rename(conf.low = `(lower`,
               conf.high = `upper)`,
               estimate = results) %>%
        filter(!str_detect(term, "(Intercept)"))

  glance_dcpoUncertainAPSR <- glance.plm(result[[1]])

  result_expAPSR <- list(tidy_dcpoUncertainAPSR, glance_dcpoUncertainAPSR)
})

names(result_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",  "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_expAPSR, file = here("output", "estimates_clsExpAPSR.RDS"))
```

```{r coefName-APSR, eval=TRUE}
index_coefName <- c(
    `plm::lag(SupDem_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(SupDem_trim, 1:2)2` = "Support[t-2]",
    `plm::lag(theta_trim, 1:2)1` = "Support[t-1]",
    `plm::lag(theta_trim, 1:2)2` = "Support[t-2]",

    `diff(Libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `diff(Vdem_libdem_z, lag = 1)` = "Delta~Liberal~democracy",
    `plm::lag(Libdem_z, 1)` = "Liberal~democracy[t-1]",
    `plm::lag(Vdem_libdem_z, 1)` = "Liberal~democracy[t-1]",

    `diff(Liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `diff(Vdem_liberal_z, lag = 1)` = "Delta~Electoral~democracy",
    `plm::lag(Liberal_z, 1)` = "Electoral~democracy[t-1]",
    `plm::lag(Vdem_liberal_z, 1)` = "Electoral~democracy[t-1]",

    `diff(Polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `diff(Vdem_polyarchy_z, lag = 1)` = "Delta~Minoritarian~democracy",
    `plm::lag(Polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",
    `plm::lag(Vdem_polyarchy_z, 1)` = "Minoritarian~democracy[t-1]",

    `diff(lnGDP_imp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `diff(lg_imp_mdpgdp, lag = 1)` = "Delta~Log~GDP~per~capita",
    `plm::lag(lnGDP_imp, 1)` = "Log~GDP[t-1]",
    `plm::lag(lg_imp_mdpgdp, 1)` = "Log~GDP[t-1]"
    # `diff(Corrup_TI_z, lag = 1)`= "Delta~Corruption",
    # `plm::lag(Corrup_TI_z, 1)` = "Log~Corruption[t-1]",
    # `Corrup_TI_z` = "Log~Corruption[t-1]"
)
```

```{r plot-mainAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", fig.width=7, fig.height=10, eval = TRUE}
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

type_model <-
  c("Original", "Uncertainty", "Uncertainty+Expanded Data")

result_apsrPooled <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$pooled1[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Pooled")

result_apsrRegime <-
  list(result_clsAPSR,
       result_pureAPSR,
       result_expAPSR) %>%
  map2_df(type_model, ~ {
    .x$`pooled-regime1`[[1]] %>%
      filter(term != "(Intercept)") %>%
      select(term, estimate, conf.low, conf.high) %>%
      mutate(model = .y)
  }) %>% 
  mutate(type = "Institution Specified")

df_plot <- bind_rows(result_apsrPooled, result_apsrRegime) %>% 
    mutate(term = index_coefName[term],
           term = factor(term, levels = unique(index_coefName)), 
           type = factor(type, levels = c("Pooled", "Institution Specified")))
